\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

This thesis presents the final work done towards obtaining my master’s degree in Embedded Systems from Delft University of Technology.
To the best of my knowledge no previous work has been conducted, exploring the feasibility of a transiently-powered battery-free robot. 


\vspace{1\baselineskip}

\noindent
I would like to express my sincere gratitude to my supervisor Przemys\l{}aw Pawe\l{}czak for his excellent guidance, never failing support and enthusiasm about this project. 
I also would like to thank Amjad Majid for letting me explore his idea of transiently-powered actuation, his constructive criticism and clever suggestions as this project evolved.
I would like to thank Sinan Yildirim for his willingness to answer any of my questions, Ioannis Protonotarios for helping me with any hardware related issues, Michel Jansen for sharing his harvester schematics and low level hardware knowledge.
I would like to thank the Nuon Solar Team for lending me one of their space grade solar panels from their 2017 Nuna9 solar car.
Furthermore, I want to thank Prof. Koen Langendoen for hosting me at the Embedded Systems group, and Javier Alonso-Mora for participating as a member of my graduation committee.
Last but not least, I specially would like to thank my family for their unconditional support, encouragements and love that helped me stay motivated during this year.

\vspace{1\baselineskip}

\noindent
Koen Schaper

\vspace{1\baselineskip}

\noindent
Delft, The Netherlands

\noindent
\today
