% This document provides the style to be used for a MSc Thesis at the
% Parallel and Distributed Systems group
\documentclass[11pt,twoside,a4paper,openright]{report}

% math packages
\usepackage{amsmath}
\usepackage{amssymb}

% textblocks for title page
\usepackage[absolute]{textpos}

% use babel for proper hyphenation
\usepackage[british]{babel}

% Graphics: different for pdflatex or dvi output, choose one
%%\usepackage[dvips]{graphicx}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}

\usepackage{epstopdf}
\usepackage{rotating}
\usepackage{subcaption}

% FONT
\usepackage[scaled=.92]{helvet}
%\usepackage{times}
\usepackage{textcomp}
\usepackage{eurosym}

% for url's use "\url{http://www.google.com/}"
\usepackage{url}
\usepackage[plainpages=false]{hyperref} 

% Table
\usepackage{threeparttable, tablefootnote}
\usepackage{tabularx}
\usepackage{multirow}

% References
\usepackage{flushend}

% Tikz
\usepackage{tikz}
\usepackage{circuitikz}


% Information that will be filled in at various points in the report
\newcommand{\reportTitle}{Transiently-powered Battery-free Robot}
\newcommand{\reportAuthor}{Koen Schaper}
\newcommand{\reportEmail}{kpschaper@gmail.com}
\newcommand{\reportUrlEmail}{\href{mailto:\reportEmail}{\reportEmail}}
\newcommand{\reportMSC}{Embedded Systems} %{Embedded Systems}{Computer Engineering}{Computer Science}{Electrical Engineering}
\newcommand{\reportDate}{\today} %TODO: Dit is de datum van uitgifte van final versie aan de afstudeer commissie 
\newcommand{\presentationDate}{15 December 2017}
\newcommand{\graduationCommittee}{
prof. dr. K.G. Langendoen (chair) & Delft University of Technology \\
dr. Przemys\l{}aw Pawe\l{}czak (supervisor) & Delft University of Technology \\
dr. Javier Alonso-Mora & Delft University of Technology \\
} % The order of listing the names: Graduation prof, supervisor(s), others ordered by title + alphabetical 
%examples: 
%prof. dr. ir. H. J. Sips (chair) & Delft University of Technology \\ 
%ir. dr. D. H. J. Epema           & Delft University of Technology \\ 
\newcommand{\reportAbstract}{
	%Small robotic platforms have become increasingly popular as an educational toy for kids and are widely used by researchers to study swarm behavior with a collective of robots.
	Collectives of miniature robots are envisioned to have future applications in surveillance, search and rescue, and exploration. 
	Before these robots can become applicable in real world applications, a fundamental challenge related to the supply of energy needs to be addressed.
	The operation time of small robots is currently limited by the energy stored in batteries.
	New advancements in batteries are not expected to happen anytime soon, as history shows that new battery technologies are slow emerging.
	This thesis proposes to replace the battery with an energy harvester and temporarily store harvested energy in a supercapacitor, which creates a new phenomenon to be taken into consideration; the intermittent availablility of energy results in frequent power interrupts.
	Intermittentcy is currently not taken into account when developing a robot, and its effect on control techniques and locomotion are unexplored.
	In this work a transiently-powered battery-free robot is developed that purely operates from harvested energy.
	Energy is harvested from light using a lighting setup consisting of four halogen lamps, making the robot is able to move with a 16\% power duty cycle.
	With the help of local feedback the robot is able to preform controlled movements, while peristent state variables enable the robot to save the movement progress across power cycles.
	The movement accuracy of the transiently-powered robot is evaluated by recording straight and curved movements, and tracking software is used to extract the exact path of movement.
	The transiently-powered robot shows minimal increased deviation from its instructed path when compared to its battery powered equal, given an experimentially determined minimum interrupt period of 0.3\,s.
	The results prove the feasablility of a transiently-powered battery-free robot, while it makes small robots self sufficient and energy autonomous.
}
\newcommand{\reportKeywords}{TODO KEYWORDS}

% For pdflatex
\pdfinfo{
   /Author (\reportAuthor)
   /Title  (\reportTitle)
   /Keywords (\reportKeywords)
}

\begin{document}

\pagenumbering{alph}
\pagestyle{empty}


% FRONTCOVER
\include{template/frontcover}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hoffset=1.63cm
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=5in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parindent=1em

% EMPTY PAGE
\cleardoublepage

\pagestyle{plain}
\pagenumbering{roman}
\setcounter{page}{1}

% TITLE PAGE: page i (hidden)
\include{template/titlepage}

% GRADUATION DATA AND ABSTRACT: pages ii and iii (hidden)
\include{template/graduationdata}
%\setcounter{page}{4}

% EMPTY PAGE: page iv
\cleardoublepage

% OPTIONAL QUOTATION: page v
%\include{quotation}
% EMPTY PAGE: page vi
%\cleardoublepage

% PREFACE: page v
\include{chapters/preface}
% EMPTY PAGE: page vi
\cleardoublepage

% TABLE OF CONTENTS: starting at page vii
\tableofcontents

\cleardoublepage

\pagenumbering{arabic}
\setcounter{page}{1}

% INTRODUCTION: page 1
\include{chapters/introduction}

% CHAPTERS ... For instance: History/Prior Work, Design/Implementation, Experiments
\include{chapters/related_work}

\include{chapters/preliminaries}

%\input{chapters/model}

\include{chapters/design_and_implementation}

\include{chapters/evaluation}

% CONCLUSIONS AND FUTURE WORK
\include{chapters/summary}

% BIBLIOGRAPHY
%#define SORTED 1
%\bibliographystyle{../bib/latex8}
%\bibliography{../bib/bibtex}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bib/bibtex,bib/non-paper}

\appendix
\include{chapters/appendix_a}

\end{document}

